Updates on the Exoplanet Orbit Database

### 2014-02-04 draft/ms.tex
Adds comments for Sec 2.1.

TEST!

@@

@@

KDE

@@

\textit{(Sharon's comments: You don't need to
  describe why we include a planet in EOD -- this is covered at the
  beginning of Section~\ref{sec:update} as we discuss the `scope of
  EOD'. Just say what this flag is. Also, right now it includes RV,
  Transit, and also some Timing planets. The first sentence sounds
  like as long as a planet is discovered via RV and transit, it'll be
  in EOD, which is not true, I think.)}

@@

\textit{(Sharon's
  comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.)}

>>>>

@@

\textit{Sharon: I don't think the first sentence is true... Looking at
  the fields in the Planet Information section in the table, it
  doesn't contain when who or how at all... The current way of
  dividing fields into these categories is a bit weird, but we are
  definitely not changing it in our paper or change the website any
  time soon... I'm guessing you want to summarize what Planet
  Information fields cover in the first sentence here, so maybe look
  at the table and give a very general summary of what those fields
  are.

  I'm not sure what's the purpose of the second sentence... It sounds
  like something we generally did for EOD. Maybe we should move it to
  the paragraph above in the overview text for
  Section~\ref{sec:update}. Think more about what the purpose of the
  subsection overview should serve.}

@@

\textit{Sharon: you need to say what KOI stores. When writing each
  field, keep in mind you need to cover the following so that the
  reader will completely understand: (1) what the field stands for
  (e.g., in case of an abbreviation like KOI); (2) what the field
  physically means, like `KOI' means planet candidates that have transit
  signals as detected by \kepler\ but have not been confirmed, and
  make sure to be thorough at what you say -- sometimes things are not
  that obvious to an outsider reader, e.g., think if a cosmologist
  would understand what you're saying when reading it; (3) what the
  field actually contains, e.g. KOI contains the KOI number designated
  by the \kepler\ team (right?), it is a floating point number, and
  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
  something...; (4) why we added this new field, if this information
  is helpful, or if it's a revised field since \cite{Wright2011}, what
  is changed.

  Also, use \keper\ (which is a defined symbol in our ms.tex file),
  instead of typing out Kepler, since you need italic.

  Don't be afraid to write more! Being concise is important, but it's
  always easier to trim down things than to add things on, especially
  for a documentation type of paper like this. Let's be thorough at
  first, then try to reach optimal conciseness. }

KDE:

@@

EOD: A planet with the EOD flag being true indicates that it has
well-characterized orbital parameters such as PER, ECC, K, OM, and I
and is thus included in the EOD. We added this field because
exoplanets.org now also includes robustly discovered planets that do
not have well-characterized orbits, and also \kepler\ planet
candidates (see Section~\ref{sec:kepler} for more details).

\textit{Sharon: I've provided my version here: the stuff I added on
  top of your writing is what I think was missing and may make a
  cosmologist wonder. ;)

  Also, EOD doesn't require the orbit to be 'Keplerian', right? We do
  include reported dynamic fits - they're definitely not
  Keplerian. Am I right?

  Note that I've covered all the 4 aspects I mentioned above. :)}

@@

\textit{Sharon: you've changed `discovered' to `detected', but it's
  still not an accurate description. Let's meet and discuss this in
  person.

  old: Sharon's
  comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.}
